The Current State of R Tools for Nonlinear Least Squares Modeling

### 2023-07-15 RefactoringNLS/revision202307/StateOfRToolsForNLS.Rmd
fixes as per AB

---
title: "The Current State of R Tools for Nonlinear Least Squares Modeling"
author:
- John C. Nash \thanks{ retired professor, Telfer School of Management, University
  of Ottawa}
- Arkajyoti Bhattacharjee \thanks{Department of Mathematics and Statistics, Indian
  Institute of Technology, Kanpur}
date: "2023-3-2"
output: 
  pdf_document:
    pandoc_args: --listings
    includes:
      in_header: preamble.tex
  word_document:
    toc: no
bibliography: ./StateOfRToolsForNLS.bib
link-citations: yes
linkcolor: red
urlcolor: blue
---

@@

```{r tetrarun}
time <- c(1,  2,  3,  4,  6 , 8, 10, 12, 16)
conc <- c(0.7, 1.2, 1.4, 1.4, 1.1, 0.8, 0.6, 0.5, 0.3)
NLSdata <- data.frame(time,conc)
NLSstart <- c(lrc1 = -2, lrc2 = 0.25, A1 = 150, A2 = 50) # a starting vector (named!)
NLSformula <- conc ~ A1 * exp(-exp(lrc1) * time) + A2 * exp(-exp(lrc2) * time)
tryit <- try(nls(NLSformula, data = NLSdata, start = NLSstart, trace = TRUE))
print(tryit)
```

>>>>

---
title: "The Current State of R Tools for Nonlinear Least Squares Modeling"
author:
- John C. Nash \thanks{ retired professor, Telfer School of Management, University
  of Ottawa}
- Arkajyoti Bhattacharjee \thanks{Department of Mathematics and Statistics, Indian
  Institute of Technology, Kanpur}
date: "2023-3-2"
output: 
  pdf_document:
    keep_tex: yes
    toc: no
  word_document:
    toc: no
bibliography: ./StateOfRToolsForNLS.bib
link-citations: yes
linkcolor: red
urlcolor: blue
---

@@

```{r tetrarun}
time <- c(1,  2,  3,  4,  6 , 8, 10, 12, 16)
conc <- c(0.7, 1.2, 1.4, 1.4, 1.1, 0.8, 0.6, 0.5, 0.3)
NLSdata <- data.frame(time,conc)
NLSstart <- c(lrc1 = -2, lrc2 = 0.25, A1 = 150, A2 = 50) # a starting vector (named!)
NLSformula <- conc ~ A1 * exp(-exp(lrc1) * time) + A2 * exp(-exp(lrc2) * time)
tryit <- try(nls(NLSformula, data = NLSdata, start = NLSstart, trace = TRUE))
# print(tryit) # gives no information on best sumsquares or model parameters
```
